To be FAIR: Theory Specification Needs an Update

### 2025-02-21 manuscript.Rmd
Make it clear that using GitHub and Zenodo actually meets ALL fair principles. closes #29

Open science infrastructure is an area of active development, and as such,
the approach proposed here should not be considered definitive,
but rather, as one proposal for a FAIR-compliant implementation of theory.
The guiding principle of our implementation is to align and build upon existing successful open science infrastructures to the maximum possible extent.
At the time of writing (2024), 
the value of using Git for version control of academic research is well-established,
and the integration of GitHub and Zenodo makes for a particularly user-friendly approach.
Zenodo and GitHub are also integrated with the Open Science Framework (OSF),
a popular platform in psychology.
Creating a front page on the OSF increases the visibility of a FAIR theory,
while the integration with Zenodo and GitHub removes the need for uploading and maintaining the same information on multiple platforms.
While we make use of specific open science infrastructures, it is important to stress that our workflow illustrates general principles which can also be implemented using other open science infrastructures.
The process described here can be largely automated in R using the `theorytools` package; see the package vignette on FAIR theory, `vignette("fairtheory", package = "theorytools")`.

>>>>

To concretize the FAIR principles,
we propose an applied workflow for making theory FAIR.
The guiding principle of our approach is to align and build upon existing successful open science infrastructures to the greatest possible extent.
At the time of writing (2024),
the value of using Git for version control of academic research is well-established [@ramGitCanFacilitate2013],
and the integration of GitHub and Zenodo makes for a particularly user-friendly approach that meets *all* of the FAIR principles (Table \@ref(tab:tabfair)).
Zenodo and GitHub are both integrated with the Open Science Framework (OSF),
a popular platform in psychology.
Thus, it is possible to create a project page on the OSF to increase the visibility of a FAIR theory amongst users of that platform,
while the integration of the OSF with Zenodo and GitHub removes the need for maintaining the same information on multiple platforms.
Note that open science infrastructure is an area of active development, and as such,
the approach proposed here is subject to change.
Nevertheless, it illustrates general principles which can also be implemented using other open science infrastructures.
Our workflow can be largely automated in R using the `theorytools` package.
For the most recent version of our proposed workflow, see the package vignette on FAIR theory, `vignette("fairtheory", package = "theorytools")`.
